\section*{Introduction}
In today’s world, online social networks (OSN) are very important media for sharing, organizing and finding contents and contacts. Analysis of such networks not only helps to reveal many interesting properties of these networks, but also it helps to improve the present systems and to design new applications of social networks. The structure of these networks changes from time to time. Moreover a lot of processes goes on over these networks. To analyze various properties of such networks, it is important to understand the underlying dynamics and various factors that drive this dynamics.

Influence between two nodes is an important factor that drive all dynamics in a social network. Therefore in order to understand the dynamics in OSNs, the influence between two nodes needs to be modeled. However, the influence that a person has on another person significantly depends on their relationship and the context in which they are. A professor at an university may not have much influence on who her student connects to, on Facebook. But, the student may be highly influenced by her professor when it comes to which piece of literature to read next. Today’s vast proliferation of online social networks (OSN) allows us to study such interactions. Here we present two learning models to address the problems of link prediction and understanding opinion propagation in OSNs.

The problem of link prediction (LP) is stated as follows: given a graph, for every vertex in the graph, find vertices to which the given vertex is most likely to form new edges. The problem of link prediction is very important, in the context of social search and recommendation. Our earlier method used two novel signals to improve accuracy in link prediction. First, we used a co-clustering algorithm to find the underlying communities in the network. We used this information to qualify edges in the graph with a surprise value. This represented how unexpected the edge is in the graph, given the underlying community structure information. Second, we computed a node to node similarity measure which takes into account the local connectivity structure between these nodes. These signals were then used in combination of others as input to a discriminative predictor to estimate likelihoods for future edges. When tested across five diverse datasets, common in link prediction literature, we find our method performs significantly better than standard link prediction methods.

However in recent times we have seen apart from just using feeding the computed node and edge scores to a top level classifier we can learn a Link function which will combine all the features. In this particular work we have mostly studied and verified the work of Aditya Krishna Menon and Charles Elkan on Link Prediction via Matrix Factorization and we propose a methodology about how we can merge both these works for a better Link Prediction Algorithm. 
